\documentclass[11pt]{article}

%Gummi|065|=)
\title{\textbf{Lab rapport in C++ OOP}}
\author{Hergeir Winther Lognberg \\
Hewi1600}
\date{}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{textcomp}

\definecolor{listinggray}{gray}{0.9}
\definecolor{lbcolor}{rgb}{0.9,0.9,0.9}
\lstset{
backgroundcolor=\color{lbcolor},
	tabsize=4,    
%   rulecolor=,
	language=[GNU]C++,
		basicstyle=\scriptsize,
		upquote=true,
		aboveskip={1.5\baselineskip},
		columns=fixed,
		showstringspaces=false,
		extendedchars=false,
		breaklines=true,
		prebreak = \raisebox{0ex}[0ex][0ex]{\ensuremath{\hookleftarrow}},
		frame=single,
		numbers=left,
		showtabs=false,
		showspaces=false,
		showstringspaces=false,
		identifierstyle=\ttfamily,
		keywordstyle=\color[rgb]{0,0,1},
		commentstyle=\color[rgb]{0.026,0.112,0.095},
		stringstyle=\color[rgb]{0.627,0.126,0.941},
		numberstyle=\color[rgb]{0.205, 0.142, 0.73},
%        \lstdefinestyle{C++}{language=C++,style=numbers}’.
}
\lstset{
	backgroundcolor=\color{lbcolor},
	tabsize=4,
  language=C++,
  captionpos=b,
  tabsize=3,
  frame=lines,
  numbers=left,
  numberstyle=\tiny,
  numbersep=5pt,
  breaklines=true,
  showstringspaces=false,
  basicstyle=\footnotesize,
%  identifierstyle=\color{magenta},
  keywordstyle=\color[rgb]{0,0,1},
  commentstyle=\color{purple},
  stringstyle=\color{red}
  }


\begin{document}

\maketitle

\section{Preamble}

Assignment was to create a Bank which operated the way the lab described.

\section{The Code}
\subsection{placement}
I've decided to keep all files associated with the lab in the root of the project folder.
\subsection{Template memberfunction definitions}
Also relevant is it that I have actually defined all template class functions in a cpp file and instantialized with double there. So that the compiler actually would know which template to compile. (hope you know what i'm trying to say)

\begin{lstlisting}
	//bottom of DataFileReader.cpp
	template class DataFileReader<double>; //instantiating template with type double
\end{lstlisting}

\subsection{namespace}
I chose to remove
\begin{lstlisting}
using namespace std;
\end{lstlisting}
from all files it was previously used in. I find that this improves readability and clearly seperates std functions from self-made ones.


Still I have not had the need (nor want) for a shared pointer. 

\section{conslusion}
I think this lab went well. And was alot easier than the previous ones (in a good way). Lots of new stuff learned but marginal amount of typing.


\section{Question}
Is it bad form to define the template member functions in the cpp files.

Was I correct in my approach?

\section{Building/Compiling}
Just run \emph{make} in the Lab directory.
To run the program run \emph{make run} in same directory.

\section{Enviroment}
I'm programming on an Arch linux 64-bit system. I've got the gcc compiler installed and compile using it's g++ alias which links necessary libraries automatically. To compile I use the recommended flags: "-std=c++11 -Wall -pedantic". The flags let me choose to use c++11 standard and give me useful compiling warnings and errors. 
For editing of code i currently use VS code with a makefile.

\section{Backup}
And if anything's missing you can find it on: \\
github: \url{https://github.com/Hergeirs/Cpp-Obj/tree/master/Level%202/Lab3} \\
\href{https://github.com/Hergeirs/Cpp-Obj/tree/master/Level%202/Lab3}{Cpp-obj/Lab2}

\flushright{\today}
\end{document}
