\documentclass[11pt]{article}
\usepackage{datetime}

%Gummi|065|=)
\title{\textbf{Project in C++ OOP}}
\author{Hergeir Winther Lognberg \\
Hewi1600}
\date{}
\begin{document}

\maketitle

\section{Preamble}

In this project I'm to code a "jukebox" terminal program that follows the specifications given from the teacher.
I've striven to make the code as clean, readable and free of redundancies as possible. Also the one specification was to use STL and I've tried to use it as much as i deemed practical. 

I'm aiming for the highest grade.

\section{The Code}

\subsection{placement}
I've decided to keep all files associated with the project in the root of the project folder. There are in all 19 files containing code and 1 file containing the jukebox database. Out of them 8 are header files (1 for each class and 1 extra for some user-defined functions. 

\subsection{code placement}
The header files do not contain code other than class definitions and function prototypes. 

I've kept all overloadings of operators at the bottom of the relevant files to keep consistent style.

In \emph{Jukebox.cpp} (the most substantial file) I've tried to make the placement of functions chronological to the menu switch statement orders. And functions not called directly by switches at the bottom of the file. 

\subsection{code}
The first thing I'll mention here is the code in the \emph{functions.cpp}. Here i keep some functions I've made myself for handling user input (\emph{getInt,getLine})


I assumed we where supposed to use c-array instead of new array class. Hope i was correct. 

Would love any feedback on good code practice. 
I wondered wether I should have used difference between index address and array address for my for loop in the printing function (\emph{printArr}). I know it would work, but am not sure wether this would be considered readable?
\newline \\
$for(int\quad*i=array;i<array+size;++i) \\
if((i-array)\%200==0) \\
cout << endl;
$
\newline \\
where \emph{array} is address to beginning of array and size is int containing its' size.
\section{Enviroment}
I'm programming on an Arch linux 64-bit system. I've got the c++ compiler installed and compile using it's g++ alias which links necessary libraries automatically. To compile i use the recommended flags: "-std=c++11 -Wall -pedantic". The flags let me choose to use c++11 standard and give me useful compiling warnings and errors. 
\flushright{\today}
\end{document}
